Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
minor update
rewrite code programmatically

```{r TODO}
# TODO: compute corrected confidence for AR
# TODO: compute lhs.support, for grade, not taken and  
```

```{r library, message = FALSE, warning = FALSE}
library(arulesSequences)

library(tidyverse)
```

@@

  # Join with transcripts.
  select(- Period) %>%
  inner_join(d_transcript, by = "Course ID") %>%

  # Identifying sequences
  rename(sequenceID = `Student ID`) %>%

  # Identifying time of event (sequence)
  mutate(
    Period  = substr(Period, 1, 1),
    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
    ) %>%

  # Identifying item
  mutate(
    PF = case_when( Grade <  pass_grade ~ "fail",
                    Grade >= pass_grade ~ "pass"),
    HL = case_when( Grade <  high_grade ~ "low",
                    Grade >= high_grade ~ "high"),

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )

@@

    taken = case_when(
      is.na(Grade) ~ "not taken",
      TRUE         ~ "taken"),

    item_taken= paste(item, taken, sep = "_"),
    item_taken_grade= case_when(
      is.na(Grade) ~ paste(item, taken, sep = "_"),
      TRUE            ~ paste(item, PF)
      )
    )

@@

d_transactions_expanded <- d_transactions %>%
  mutate(Round_grade = round(Grade, 0),
         Values = T) %>%
  spread(key = "Round_grade", value = Values) %>%
  mutate(`1`  = `0`|`1`,
         `2`  = `1`|`2`,
         `3`  = `2`|`3`,
         `4`  = `3`|`4`,
         `5`  = `4`|`5`,
         `6`  = `5`|`6`,
         `7`  = `6`|`7`,
         `8`  = `7`|`8`,
         `9`  = `8`|`9`,
         `10`  = `9`|`10`
         ) %>%
  gather(key = "Grade_round", value = "Gr_bool", `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, na.rm = TRUE, convert = TRUE) %>%
  select(-Gr_bool) %>%
  arrange(
    sequenceID,
    item
  ) %>%

  # Identifying item
  mutate(
    PF = case_when( Grade_round <  pass_grade ~ "fail",
                    Grade_round >= pass_grade ~ "pass"),
    HL = case_when( Grade_round <  high_grade ~ "low",
                    Grade_round >= high_grade ~ "high"),

    item_PF = paste(item, PF, sep = "_"),
    item_HL = paste(item, HL, sep = "_"),
    item_Grade = paste(item, Grade_round, sep = "_")
    )
```

>>>>

```{r TODO}
# TODO: compute corrected confidence for AR
# TODO: compute lhs.support, for grade
```

```{r library, message = FALSE, warning = FALSE}
library(tidyverse)
library(arulesSequences)
```

@@

  # Join with transcripts.
  select(- Period) %>%
  inner_join(
    d_transcript,
    by = "Course ID"
    ) %>%

  # Identifying sequenceID
  rename(sequenceID = `Student ID`) %>%

  # Identifying evenID
  mutate(
    Period  = substr(Period, 1, 1),
    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
    ) %>%

  # Identifying itemID
  mutate(
    PF = case_when( Grade <  pass_grade ~ "fail",
                    Grade >= pass_grade ~ "pass"),
    HL = case_when( Grade <  high_grade ~ "low",
                    Grade >= high_grade ~ "high"),

    item    = `Course ID`,
    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    )

@@

    taken = case_when(
      is.na(Grade) ~ "not taken",
      TRUE         ~ "taken"
      ),

    taken_grade = case_when(
      is.na(Grade) ~ "not taken",
      Grade < 5.5  ~ "fail",
      TRUE         ~ "pass"
      ),

    item_taken       = paste(item, taken      , sep = "_"),
    item_taken_grade = paste(item, taken_grade, sep = "_")

@@

d_transactions_grade <- d_transactions %>%

  # Spread along rounded grades
  mutate(
    Round_grade = round(Grade, 0),
    Values = TRUE
    ) %>%
  spread(
    key   = Round_grade, 
    value = Values
    ) %>%

  # fill grades inferior to obtained grade with TRUE
  mutate(
    `1`  = `0`|`1`,
    `2`  = `1`|`2`,
    `3`  = `2`|`3`,
    `4`  = `3`|`4`,
    `5`  = `4`|`5`,
    `6`  = `5`|`6`,
    `7`  = `6`|`7`,
    `8`  = `7`|`8`,
    `9`  = `8`|`9`,
    `10` = `9`|`10`
    ) %>%

  # Gather along rounded grades
  gather(
    key = Grade_round,
    value = "Gr_bool",
    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
    na.rm = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -Gr_bool
    )%>%

  # Arrange per sequenceID and item for making sequences
  arrange(
    sequenceID,
    item
    ) %>%

  # Identifying item
  mutate(
    item_Grade = paste(item, Grade_round, sep = "_")
    )
```
